\textsc{Beyond the Iceberg Hypothesis: \\Opening the Black Box of Transport Costs}

### 2017-12-19 redaction/dhp_july2017.tex
J’ai juste changé ma signature
Je ne sais pas pourquoi cela donne tout comme changé.

\title{\textsc{Beyond the Iceberg Hypothesis: \\Opening the Black Box of Transport Costs}\thanks{We are grateful to participants at ETSG 17\textsuperscript{th} meetings in Helsinki, DEGIT XXII in Paris School of Economics, and participants at seminars of the University of California-Irvine, the Universities of Paris-Dauphine Paris-I and Nancy for very useful discussions. Finally, any remaining errors are ours. This paper features an online appendix containing additional results and available on the authors' websites.}}
\author{Guillaume \textsc{Daudin}\thanks{%
Universit\'{e} Paris-Dauphine, PSL Research University, LEDa-DIAL, UMR 225, France \& Sciences Po, Observatoire Fran\c{c}ais des Conjonctures \'{E}conomiques (OFCE), France; email: \url{guillaume.daudin@dauphine.fr}}  \qquad J\'{e}r\^{o}me \textsc{H\'{e}ricourt} \thanks{Universit\'{e} de Lille - LEM-CNRS UMR 9221, France \& CEPII, France; email: \url{jerome.hericourt@univ-lille1.fr}}\qquad Lise \textsc{Patureau}\thanks{Corresponding author. Universit\'{e} Paris-Dauphine, PSL Research University, LEDa, France;  email: \url{lise.patureau@dauphine.fr} } }

>>>>

\title{\textsc{Beyond the Iceberg Hypothesis: \\Opening the Black Box of Transport Costs}\thanks{We are grateful to participants at ETSG 17\textsuperscript{th} meetings in Helsinki, DEGIT XXII in Paris School of Economics, and participants at seminars of the University of California-Irvine, the Universities of Paris-Dauphine Paris-I and Nancy for very useful discussions. Finally, any remaining errors are ours. This paper features an online appendix containing additional results and available on the authors' websites.}}
\author{Guillaume \textsc{Daudin}\thanks{%
Universit\'{e} Paris-Dauphine, PSL Research University, LEDa, 75016 PARIS, FRANCE \newline
Universit\'{e} Paris-Dauphine, PSL Research University, IRD, LEDa, UMR 225, DIAL, 75016 PARIS, FRANCE \newline
Sciences Po, Observatoire Fran\c{c}ais des Conjonctures \'{E}conomiques (OFCE), 75014 PARIS, FRANCE \newline
; email: \url{guillaume.daudin@dauphine.fr}}  \qquad J\'{e}r\^{o}me \textsc{H\'{e}ricourt} \thanks{Universit\'{e} de Lille - LEM-CNRS UMR 9221, France \& CEPII, France; email: \url{jerome.hericourt@univ-lille1.fr}}\qquad Lise \textsc{Patureau}\thanks{Corresponding author. Universit\'{e} Paris-Dauphine, PSL Research University, LEDa, France;  email: \url{lise.patureau@dauphine.fr} } }
